Model LF

### 2022-11-01 Estimation.Rmd
Commit

```{r}
reg_prod_start=dynlm(TSDELTALOG(prod_ds) ~ 1 + L(TSDELTALOG(prod_ds),1:4) +  L(TSDELTALOG(wage_ds),0:4)+  L(TSDELTALOG(mean_dp_regul),0:4) +  L(TSDELTALOG(y_ds),0:4) + L(log(prod_ds),1)+ L(log(y_ds),1) + L(log(wage_ds),1)+ L(log(mean_dp_regul),1))

@@

```{r}
reg_prod=dynlm(TSDELTALOG(prod_ds) ~ 0 + L(TSDELTALOG(prod_ds),c(4)) +  L(TSDELTALOG(wage_ds),0) +  L(TSDELTALOG(y_ds),0) + L(log(prod_ds),1)+ L(log(y_ds),1) + L(log(wage_ds),1)+ L(log(mean_dp_regul),1))

>>>>

```{r}
reg_prod_start=dynlm(TSDELTALOG(prod_ds) ~ 1 + L(TSDELTALOG(prod_ds),1:4) +  L(TSDELTALOG(mean_dp_regul),0:4) +  L(TSDELTALOG(y_ds),0:4) + L(log(prod_ds),1)+ L(log(y_ds),1) + L(log(mean_dp_regul),1))

@@

```{r}
reg_prod=dynlm(TSDELTALOG(prod_ds) ~ 0 + L(TSDELTALOG(prod_ds),c(4)) +  L(TSDELTALOG(y_ds),0) + L(log(prod_ds),2)+ L(log(y_ds),2) + L(log(mean_dp_regul),2))

### 2022-11-01 prod test.Rmd
Commit

COMMENT> 
BEHAVIORAL> prod_ds_shock
TSRANGE 2006 3 2020 1
EQ> TSDELTALOG(prod_ds_shock) =  pr_1* TSDELTALOG(y_ds) + pr_2* TSDELTALOG(TSLAG(y_ds,1)) + pr_3* TSDELTALOG(TSLAG(prod_ds_shock,1)) + pr_4* TSDELTALOG(TSLAG(prod_ds_shock,4))+ pr_5* LOG(TSLAG(y_ds,1))  + pr_8* LOG(TSLAG(dp_person,1)) + pr_9* TSLAG(s_h,1) + pr_10* LOG(TSLAG(prod_ds_shock,1))
COEFF> pr_1 pr_2 pr_3 pr_4 pr_5 pr_8 pr_9 pr_10
STORE> coe(222)

>>>>

COMMENT> 
BEHAVIORAL> prod_ds_shock
TSRANGE 2006 3 2020 1
EQ> TSDELTALOG(prod_ds_shock) = + pr_1* TSDELTALOG(wage_ds) +
pr_2* TSDELTALOG(TSLAG(y_ds,4)) +
pr_3* TSDELTALOG(y_ds) + 
pr_8* LOG(TSLAG(y_ds,2))  +
pr_9* LOG(TSLAG(dp_person,2)) +
pr_10* LOG(TSLAG(prod_ds_shock,2))+
pr_11* LOG(TSLAG(wage_ds,2))
COEFF>  pr_1 pr_2 pr_3 pr_8 pr_9 pr_10 pr_11
STORE> coe(222)
